```latex
\documentclass[10pt, letterpaper]{article}

\usepackage[
    ignoreheadfoot,
    top=1.5cm,
    bottom=0.3cm,
    left=1.5cm,
    right=1.5cm,
    footskip=1.0cm,
]{geometry}
\usepackage[explicit]{titlesec}
\usepackage{tabularx}
\usepackage{array}
\usepackage[dvipsnames]{xcolor}
\definecolor{primaryColor}{RGB}{0, 79, 144}
\usepackage{enumitem}
\usepackage{fontawesome5}
\usepackage{amsmath}
\usepackage[
    colorlinks=true,
    urlcolor=primaryColor
]{hyperref}
\usepackage[pscoord]{eso-pic}
\usepackage{calc}
\usepackage{bookmark}
\usepackage{lastpage}
\usepackage{changepage}
\usepackage{paracol}
\usepackage{ifthen}
\usepackage{needspace}
\usepackage{iftex}

\ifPDFTeX
    \input{glyphtounicode}
    \pdfgentounicode=1
    \usepackage[T1]{fontenc}
    \usepackage[utf8]{inputenc}
    \usepackage{lmodern}
\fi

\usepackage[default, type1]{sourcesanspro}

\AtBeginEnvironment{adjustwidth}{\partopsep0pt}
\pagestyle{empty}
\setcounter{secnumdepth}{0}
\setlength{\parindent}{0pt}
\setlength{\topskip}{0pt}
\setlength{\columnsep}{0.15cm}

\makeatletter
\let\ps@customFooterStyle\ps@plain
\patchcmd{\ps@customFooterStyle}{\thepage}{
    \color{gray}\textit{\small Name - Page \thepage{} of \pageref*{LastPage}}
}{}{}
\makeatother
\pagestyle{customFooterStyle}

\titleformat{\section}{
    \needspace{4\baselineskip}
    \Large\color{primaryColor}
}{}{
}{
    \textbf{#1}\hspace{0.15cm}\titlerule[0.8pt]\hspace{-0.1cm}
}[]

\titlespacing{\section}{-1pt}{0.3cm}{0.2cm}

\newenvironment{highlights}{
    \begin{itemize}[
        topsep=0.15cm,
        parsep=0.15cm,
        partopsep=0pt,
        itemsep=0.1cm,
        leftmargin=0.4cm + 10pt
    ]
}{
    \end{itemize}
}

\newenvironment{highlightsforbulletentries}{
    \begin{itemize}[
        topsep=0.15cm,
        parsep=0.15cm,
        partopsep=0pt,
        itemsep=0.1cm,
        leftmargin=10pt
    ]
}{
    \end{itemize}
}

\newenvironment{onecolentry}{
    \begin{adjustwidth}{0.2cm + 0.00001cm}{0.2cm + 0.00001cm}
}{
    \end{adjustwidth}
}

\newenvironment{twocolentry}[2][]{
    \onecolentry
    \def\secondColumn{#2}
    \setcolumnwidth{\fill, 4.5cm}
    \begin{paracol}{2}
}{
    \switchcolumn \raggedleft \secondColumn
    \end{paracol}
    \endonecolentry
}

\newenvironment{threecolentry}[3][]{
    \onecolentry
    \def\thirdColumn{#3}
    \setcolumnwidth{1cm, \fill, 4.5cm}
    \begin{paracol}{3}
    {\raggedright #2} \switchcolumn
}{
    \switchcolumn \raggedleft \thirdColumn
    \end{paracol}
    \endonecolentry
}

\newenvironment{header}{
    \setlength{\topsep}{0pt}\par\kern\topsep\centering\color{primaryColor}\linespread{1.5}
}{
    \par\kern\topsep
}

\let\hrefWithoutArrow\href
\renewcommand{\href}[2]{\hrefWithoutArrow{#1}{\ifthenelse{\equal{#2}{}}{ }{#2 }\raisebox{.15ex}{\footnotesize \faExternalLink*}}}

\begin{document}

\begin{header}
    \fontsize{30pt}{30pt}
    \textbf{Muhammad Usman}

    \vspace{0.3cm}

    \normalsize
    \mbox{\hrefWithoutArrow{mailto:usmanmuhammad.riaz00@gmail.com}{{\footnotesize\faEnvelope[regular]} usmanmuhammad.riaz00@gmail.com}}%
    \kern 0.25cm%
    \mbox{\href{https://linkedin.com/in/Muhammad Usman}{{\footnotesize\faLinkedin} LinkedIn}}%
    \kern 0.25cm%
    \mbox{\href{https://github.com/Muhammad Usman}{{\footnotesize\faGithub} Github}}%
    \kern 0.25cm%
    \mbox{\hrefWithoutArrow{tel:+923004389966}{{\footnotesize\faPhone} +923004389966}}%
\end{header}

\section{Profile}
\begin{onecolentry}
    Experienced software engineer and AI developer specializing in full-stack development, machine learning, and systems programming. Adept at designing and implementing AI-powered applications and high-performance systems. Eager to leverage expertise in HTML/CSS, code review, and QA to ensure high standards in AI-generated code evaluations.
\end{onecolentry}

\section{Projects}
\begin{twocolentry}{\textbf{Streamlit, FastAPI, LangChain, ChromaDB, OpenAI GPT-4/3.5, Anthropic Claude}}
    \textbf{AI-Powered Digital Forensic Investigator}
    \begin{highlights}
        \item Architected and implemented a Retrieval-Augmented Generation (RAG) chat assistant using Streamlit, FastAPI, LangChain, and ChromaDB.
        \item Designed modular components (ChatManager, FileManager, RAGSystem) for scalable document ingestion and conversational QA.
        \item Integrated multi-model support (OpenAI GPT-4/3.5, Anthropic Claude) with source attribution and conversation memory.
    \end{highlights}
\end{twocolentry}

\begin{twocolentry}{\textbf{Streamlit, Googletrans, gTTS, TensorFlow, DistilBERT}}
    \textbf{Filmception: Movie Summary Translator \& Genre Predictor}
    \begin{highlights}
        \item Developed a multilingual movie summary translator and TTS system with Googletrans and gTTS in a Streamlit interface.
        \item Built a DistilBERT-based multi-label genre classifier in TensorFlow, tuning thresholds to optimize F1 score.
        \item Enhanced user experience with tabbed UI, progress feedback, and audio playback.
    \end{highlights}
\end{twocolentry}

\begin{twocolentry}{\textbf{Pandas, PyTorch}}
    \textbf{AI-Powered Vulnerability Scanner \& Remediator}
    \begin{highlights}
        \item Processed NVD JSON feeds with Pandas, extracting CVE details and mapping CVSS scores to severity labels.
        \item Trained and evaluated a PyTorch neural network (SeverityClassifierNN) for vulnerability severity classification.
        \item Orchestrated end-to-end data pipelines in Jupyter notebooks and handled large-scale JSON parsing.
    \end{highlights}
\end{twocolentry}

\begin{twocolentry}{\textbf{YouTube transcript API, Whisper STT, Google Gemini}}
    \textbf{YouTube Video Summarizer \& Q-A Tool}
    \begin{highlights}
        \item Built a CLI tool integrating YouTube transcript API, Whisper STT, and Google Gemini for summary and interactive Q\&A.
        \item Developed robust URL parsing, transcript fetching, and prompt templates.
        \item Optimized dependency management with lazy imports to reduce user overhead.
    \end{highlights}
\end{twocolentry}

\begin{twocolentry}{\textbf{C++}}
    \textbf{Library Management System}
    \begin{highlights}
        \item Implemented a role-based CLI application in C++ with classes for Administrator, Librarian, Student, and Janitor.
        \item Developed a hash-chain mechanism for data integrity in persistent storage.
    \end{highlights}
\end{twocolentry}

\begin{twocolentry}{\textbf{C++, Raylib, pthreads}}
    \textbf{Ludo Game}
    \begin{highlights}
        \item Created a graphical Ludo game in C++ using Raylib and pthreads for multithreading.
        \item Designed a semaphore-driven synchronization scheme for concurrent player threads.
    \end{highlights}
\end{twocolentry}

\section{Achievements}
\begin{onecolentry}
    \begin{highlights}
        \item 2nd Place, AI Hackathon (2023): AIO
        \item 2nd Place, CTF Competition (2024): FAST Cyber Society
        \item 3rd Place, Voice Agent Hackathon (2025): Trillet.ai
    \end{highlights}
\end{onecolentry}

\section{Educational Background}
\begin{twocolentry}{\textbf{NUCES (FAST), Islamabad} \\ \textit{2022 – 2026}}
    \textbf{Bachelor of Science, Cyber Security}
    \begin{highlights}
        \item Specialized coursework in Artificial Intelligence and Cyber Security.
    \end{highlights}
\end{twocolentry}

\section{Technologies}
\begin{onecolentry}
    \textbf{Languages:} Python, C++, HTML, CSS \\
    \textbf{Frameworks \& Libraries:} Streamlit, FastAPI, LangChain, TensorFlow, PyTorch, Raylib \\
    \textbf{AI \& NLP:} OpenAI GPT, Anthropic Claude, Google Gemini, Whisper, transformer-based models \\
    \textbf{Data \& Storage:} Pandas, ChromaDB \\
    \textbf{DevOps \& Tooling:} Docker, Git, Jupyter Notebook, CLI design
\end{onecolentry}

\end{document}
```